Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model

### 2014-04-07 trunk/paper_enahpc14/paper.tex
Manuel's changes
adds Pilatus results

\title{Evaluating the Performance  and Energy Efficiency of COSMO-ART,
  a Fully Online Coupled Model System with Numerical Weather
    Forecast and Chemical Transport Models }
% \thanks{This work was supported by the EU Project FP7 318793 ``EXA2GREEN''}}
%\subtitle{Write here subtitle}

@@

%\begin{figure*}
%  \includegraphics[width=0.4\textwidth]{Figs/earth.eps}
%  \caption{Please write your figure caption here}
%  \label{fig:1}
%\end{figure*}

%\begin{table}
%  \caption{Please write your table caption here}
%  \label{tab:1}
%  \begin{tabular}{lll}
%    \hline\noalign{\smallskip}
%    first & second & third  \\
%    \noalign{\smallskip}\hline\noalign{\smallskip}
%    number & number & number \\
%    number & number & number \\
%    \noalign{\smallskip}\hline
%  \end{tabular}
%\end{table}

>>>>

\title{Evaluating the Performance  and Energy Efficiency of COSMO-ART,
  a Coupled Numerical Weather Forecast and Chemical Transport Model}
% \thanks{This work was supported by the EU Project FP7 318793 ``EXA2GREEN''}}
%\subtitle{Write here subtitle}

@@
